Conversations in time: interactive visualisation to explore structured temporal data

### 2020-08-28 tsibbletalk.Rmd
done with shared tsibble

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The University of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: references.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

Lastly, three graphics are composed as an ensemble of coordinated views for multi-facetted exploration, shown as Figure \ref{fig:tourism-linking-fig} (the interactive realisation of Figure \ref{fig:highlight-retail}). Routine functions bring about new interaction with temporal data on the client side (i.e. without Shiny).

@@

Since all plots are stemmed from one shared tsibble data source, they are self-linking views. Nodes, lines, and points are clickable. For example, selecting the leaf node "Melbourne" fires up four respective series of the `Purpose` category in other subplots, characterised by "categorical linking". Press the "Shift" key to switch on persistent selection, and simultaneously select the parent node "Western Australia" to trigger its children. The domestic tourism performance in Melbourne can be quickly compared against the whole state of Western Australia. It makes navigation simpler than conditional panels, and also enables persistent selection for comparisons across groups.

>>>>

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The University of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

Lastly, three graphics are composed as an ensemble of coordinated views for multi-facetted exploration, shown as Figure \ref{fig:tourism-linking-fig} (the interactive realisation of Figure \ref{fig:highlight-retail}). Routine functions bring about new interaction with temporal data on the client side.

@@

Since all plots are stemmed from one shared tsibble data source, they are self-linking views. Nodes, lines, and points are hoverable and clickable. Given the `spec`, clicking either one element in any plot highlights all points that match the `Region` category, briefly "categorical linking". In Figure \ref{fig:tourism-linking-fig}, when hovering and selecting the circle associated with "Sydney" in the scatter plot, all data records with shared values of "Sydney" listen and react to this interaction via self updating in red. In order for comparison with other regions or states, press the "Shift" key to enable persistent selection, and simultaneously select the parent node on the tree, saying "Western Australia", to include all the children by switching to the blue colour. The domestic tourism sees Sydney as one of the most popular destinations in realm of business and friends visiting over years. Despite of relatively weaker performance in Western Australia, Australia's North West region sees the strongest upward trend, bypassing Sydney in some years.

In summary, shared tsibble data nicely bridges between the \CRANpkg{crosstalk} and **tidyverts** ecosystems. The `as_shared_tsibble()` provides a symbolic user interface for effortless construction of a hybrid of hierarchical and categorical linkings. And the `plotly_key_tree()` in turn decodes the specification to plot a tree for data overview and navigation, accompanied with more detailed plots.

### 2020-08-28 tsibbletalk.tex
done with shared tsibble

% !TeX root = RJwrapper.tex
\title{Conversations in time: interactive visualisation to explore
structured temporal data}
\author{by Earo Wang, Dianne Cook}

@@

\begin{Schunk}
\begin{Sinput}
tourism_feat <- tourism_shared %>%
  features(Trips, feat_stl)
p_br <- tourism_feat %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_year)) +
  geom_point(aes(group = Region))
\end{Sinput}
\end{Schunk}

Lastly, three graphics are composed as an ensemble of coordinated views
for multi-facetted exploration, shown as Figure
\ref{fig:tourism-linking-fig} (the interactive realisation of Figure
\ref{fig:highlight-retail}). Routine functions bring about new
interaction with temporal data on the client side (i.e.~without Shiny).

@@

Since all plots are stemmed from one shared tsibble data source, they
are self-linking views. Nodes, lines, and points are clickable. For
example, selecting the leaf node ``Melbourne'' fires up four respective
series of the \texttt{Purpose} category in other subplots, characterised
by ``categorical linking''. Press the ``Shift'' key to switch on
persistent selection, and simultaneously select the parent node
``Western Australia'' to trigger its children. The domestic tourism
performance in Melbourne can be quickly compared against the whole state
of Western Australia. It makes navigation simpler than conditional
panels, and also enables persistent selection for comparisons across
groups.

@@

\bibliography{references.bib}

\address{%
Earo Wang\\
The University of Auckland\\
Department of Statistics\\ The University of Auckland\\ New Zealand\\
}
\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}

\address{%
Dianne Cook\\
Monash University\\
Department of Econometrics and Business Statistics\\ Monash
University\\ Australia\\
}
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}

>>>>

% !TeX root = RJwrapper.tex
\title{Conversations in time: interactive visualisation to explore
structured temporal data}
\author{by Earo Wang and Dianne Cook}

@@

\begin{Schunk}
\begin{Sinput}
tourism_feat <- tourism_shared %>%
  features(Trips, feat_stl)
p_br <- tourism_feat %>%
  ggplot(aes(x = trend_strength, y = seasonal_strength_year)) +
  geom_point(aes(group = Region), alpha = .8, size = 2)
\end{Sinput}
\end{Schunk}

Lastly, three graphics are composed as an ensemble of coordinated views
for multi-facetted exploration, shown as Figure
\ref{fig:tourism-linking-fig} (the interactive realisation of Figure
\ref{fig:highlight-retail}). Routine functions bring about new
interaction with temporal data on the client side.

@@

Since all plots are stemmed from one shared tsibble data source, they
are self-linking views. Nodes, lines, and points are hoverable and
clickable. Given the \texttt{spec}, clicking either one element in any
plot highlights all points that match the \texttt{Region} category,
briefly ``categorical linking''. In Figure
\ref{fig:tourism-linking-fig}, when hovering and selecting the circle
associated with ``Sydney'' in the scatter plot, all data records with
shared values of ``Sydney'' listen and react to this interaction via
self updating in red. In order for comparison with other regions or
states, press the ``Shift'' key to enable persistent selection, and
simultaneously select the parent node on the tree, saying ``Western
Australia'', to include all the children by switching to the blue
colour. The domestic tourism sees Sydney as one of the most popular
destinations in realm of business and friends visiting over years.
Despite of relatively weaker performance in Western Australia,
Australia's North West region sees the strongest upward trend, bypassing
Sydney in some years.

In summary, shared tsibble data nicely bridges between the
\CRANpkg{crosstalk} and \textbf{tidyverts} ecosystems. The
\texttt{as\_shared\_tsibble()} provides a symbolic user interface for
effortless construction of a hybrid of hierarchical and categorical
linkings. And the \texttt{plotly\_key\_tree()} in turn decodes the
specification to plot a tree for data overview and navigation,
accompanied with more detailed plots.

@@

\bibliography{tsibbletalk.bib}

\address{%
Earo Wang\\
The University of Auckland\\%
Department of Statistics\\ The University of Auckland\\ New Zealand\\
%
%
%
\\\href{mailto:earo.wang@auckland.ac.nz}{\nolinkurl{earo.wang@auckland.ac.nz}}
}

\address{%
Dianne Cook\\
Monash University\\%
Department of Econometrics and Business Statistics\\ Monash
University\\ Australia\\
%
%
%
\\\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}
}
